Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Speeling
Roman minimise

\newcommand{\eachOccursExactlyOnce}{\mathrm{eachOccursExactlyOnce}}
\newcommand{\allDifferent}{\mathrm{allDifferent}}

@@

%
% optimisation criteria 10
%
\begin{flalign}
    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChanges  \label{eq22} \\
& minimise(\totalBoatChanges) \label{eq23}
\end{flalign}

@@

\noindent
We then capture the maxmum imbalance over all skippers (\ref{balAllA} and \ref{balAllB}) and minimise this (\ref{balAllC}). As before, the decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.

\begin{flalign}
    & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
& \maxImbalance = maximum(\imbalance) \label{balAllB} \\
& minimise(\maxImbalance) \label{balAllC}
\end{flalign}

>>>>

\newcommand{\eachOccursExactlyOnce}{\mathrm{eachOccursExactlyOnce}}
\newcommand{\allDifferent}{\mathrm{allDifferent}}
\newcommand{\minimise}{\mathrm{minimise}}

@@

%
% optimisation criteria 10
%
\begin{flalign}
    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChanges  \label{eq22} \\
& \minimise(\totalBoatChanges) \label{eq23}
\end{flalign}

@@

We then capture the maximum imbalance over all skippers (\ref{balAllA} and
\ref{balAllB}) and minimise this (\ref{balAllC}). As before, the decision
variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry
breaking is imposed at top of search.

\begin{flalign}
    & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
& \maxImbalance = maximum(\imbalance) \label{balAllB} \\
& \minimise(\maxImbalance) \label{balAllC}
\end{flalign}
